\section{User Stories}
\begin{table}[htbp]
\centering
\small
\begin{tabularx}{\textwidth}{|l|l|p{1cm}|X|X|}
\hline
\textbf{ID} & \textbf{Points} & \textbf{As a [user type]} & \textbf{I want [functionality]} & \textbf{So that [value]} \\ \hline
S1 & 2 & Player & to create an account & I can save my data/stats from playing Go Fish \\ \hline
S2 & 2 & Player & to be able to join for ONE session & I can still play with my friends until I log out \\ \hline
S3 & 1 & Player & to be prompted to either create a new account or log into a pre-existing account & I can have security in my account and save my prior progress made \\ \hline
S4 & 2 & Player & to be able to securely log out of my account & I can leave the program whenever I need to and come back/not be trapped to that single session \\ \hline
S5 & 3 & Player & to have a main menu & I can easily access my key features \\ \hline
S6 & 2 & Player & to be able to obtain currency from Go Fish games & I can make wagers or purchase other things in the hotel \\ \hline
S7 & 2 & Player & to be able to enter the username of the friend I want to add & I can have easier access to them (messaging, inviting, etc) \\ \hline
S8 & 3 & Player & to see who has previously requested to be my friend & I can accept/decline new requests I have \\ \hline
S9 & 2 & Player & to be able to remove unwanted friends & I can properly manage my "friends" \\ \hline
S10 & 3 & Player & to be able to invite my friend to my lobby & I can streamline the process of typing out the code through direct messaging \\ \hline
S11 & 3 & Player & to be able to send my friends currency & My friend can use it at the shop or in-game \\ \hline
S12 & 3 & Player & access to the shop in my main menu & I can purchase new icons or other cosmetics \\ \hline
S13 & 1 & Player & to be able to change my player icon & I can express myself through cool icons! \\ \hline
S14 & 2 & Player & to be able to message my friends in private & I can send specific information, such as my lobby code (or theirs) to them \\ \hline
S15 & 2 & Player & to be able to message the whole lobby & I can interact with others/ask questions if needed \\ \hline
\end{tabularx}
\end{table}

\pagebreak
\begin{table}[h!]
\centering
\small
\begin{tabularx}{\textwidth}{|l|l|p{1cm}|X|X|}
\hline
\textbf{ID} & \textbf{Points} & \textbf{As a [user type]} & \textbf{I want [functionality]} & \textbf{So that [value]} \\ \hline
S16 & 3 & Player & to be trained by a tutorial bot & I can learn how to play Go Fish \\ \hline
S17 & 5 & Player & to be able to create a private lobby & Other players I personally want to invite can join \\ \hline
S18 & 5 & Player & to be able to create a public lobby & Other players can join and play with me \\ \hline
S19 & 5 & Player & to be able to join a lobby based on a login code & I can play with my friends online \\ \hline
S20 & 5 & Player & to be able to join an open lobby & I can play with other players online \\ \hline
S21 & 5 & Admin & to manage other players & Games are being run smoothly \\ \hline
S22 & 2 & Admin & to be able to check on players' chat logs & Admin can check for any profanity or harassment in the chats \\ \hline
S23 & 5 & Admin & to be able to ban misbehaving players & I can ensure the safety of others \\ \hline
S24 & 1 & Admin & to be able to queue up when ready to start the game & I can start playing when everyone is ready \\ \hline
S25 & 3 & Admin & to bet hotel credits during Go Fish & I can use these credits at the hotel \\ \hline
S26 & 2 & Admin & to check all the cards I have in my deck & I can see what move to make next \\ \hline
S27 & 8 & Admin & to ask other players if they have a specific rank & I can add those cards to my deck or Go Fish \\ \hline
S28 & 1 & Admin & to see my overall wins and losses & I can compare my record with others \\ \hline
\end{tabularx}
\caption{Original user stories after revision.}
\end{table}

\pagebreak
\subsection{New User Stories}
\begin{itemize}
    \item \textbf{S2: Joining as Guest} \\
    To allow players to participate in a session without creating an account, enhancing accessibility.
    \item \textbf{S13: Change Icons} \\
    Players can now customize their accounts and have some sense of personalization while playing.
    \item \textbf{S7-11: Adding and Managing Friends} \\
    This is important for enhancing social features, improving player interaction and retention.
    \item \textbf{S24: Game Queue Up} and \textbf{S26: View Cards} \\
    Clarifying these features supports better user experience during gameplay.
    \item \textbf{S21: Admin} and \textbf{S22: Message Admin} and \textbf{S23: Admin Bans} \\
    Allowing for moderation and a sense of order while playing the game. Also helps in getting admin support if a user needs it.
\end{itemize}

After receiving feedback for our first submission of user stories we realized that there was more work to be done. Thus, we added new stories and reviewed old ones in order to improve their relevancy to the users and overall quality. Some of the new user stories that were added include making a guest account, new admin capabilities, and having a friends list. 

The reasoning behind these changes is to allow players to participate in a session without the need to create an account and for them to have better customization and overall features. The inclusion of enhanced admin features such as banning accounts improves the platform’s moderation capabilities, ensuring a safer gaming environment.

\pagebreak
\subsection{Updated stories}
\begin{itemize}
    \item \textbf{S4: Logging Out} \\
    Now rated with 2 points instead of 1.
    \item \textbf{S5: HUB / Menu} \\
    New Title: Provides a clearer description of the functionality.
    \item \textbf{S3: Logging in} and \textbf{S4: Logging out} \\
    Clarifying the login/logout process, specifying the use of email or Google authentication for security.
    \item \textbf{S6: Virtual Currency} \\
    Now has a clearer description to highlight its role in enabling players to wager or purchase items.
    \item \textbf{S14 and S15: Private/Public Messaging} \\
    Now separated into 2 different stories, effectively sliced for better comprehension and easier to resolve them one at a time.
    \item \textbf{S16 - 20: Private and Public Lobbies} \\
    Now has a clearer description to highlight its role in enabling players to wager or purchase items.
\end{itemize}
Some of the old stories that underwent change were having a card deck, games running concurrently, creating private and public lobbie, and messaging. This structure improves the clarity of the user flow and establishes a more logical sequence for tasks. 

It also assists in enhancing the clarity and usability of the descriptions, thus, helping developers and stakeholders understand functionality better. With improving messaging and the creation of lobbies, it is important for enhancing social features which promotes player interaction and retention. These changes improve the clarity of the user flow and establish a more logical sequence for tasks. \\

After revisions, we delegated the user stories amongst ourselves as follows...

\begin{itemize}
    \item Silas (16pts): S1-S6, S13, S23 (User authentication / account creation, main menu, changing icons, main menu, and admin bans)
    \item Marley (18pts): S12, S24-28 (Creating the shop and all of the main game features)
    \item Ryland (22pts): S8-S11, S14, S15, S21, S22 (All stories relating to friend editing/requests and all of messaging)
    \item Chase (25pts): S7, S16-S20 (Adding a friend from requests, tutorial on how to play, and everything dealing with creating both private and public lobbies)
\end{itemize}