\section{Sprint Planning \& Retrospective}
\subsection{Team Speed (story points per sprint)}
\begin{itemize}
    \item Silas: 10 points for 13 hours; ~0.769 hours per point
    \item Marley: 
    \item Ryland: 10 points for 10 hours; 1 hour per point
    \item Chase: 9 points for 8 hours; 1.125 hours power point
    \item \textbf{Total Points: }
\end{itemize}

\subsection{Barriers Along the Way/Spikes}
We ran into many obstacles throughout this second sprint. Most recently we had troubles with Jest and testing our application. At first we were able to install the necessary packages and test basic functions. However, after further investigation and deeper digging we were able to get Jest working by utilizing React Testing Library to get the testing portion working. Furthermore, we ran into trouble within GitHub as we were all working on the same repository. While we were able to create branches off of the main branch and work on our own tasks, we ran into a lot of merge conflicts and even problems with committing and pushing to the main branch in general. Another problem we ran into was retrieving from and updating our database, whether this be account creation/logging in and out of an account or setting up a listener for the database to send and receive private messages. This was most apparent with features that required real-time updates from the database as this further complicated how we would display the data. This also proved troublesome in testing as we could not figure out how to check in real-time updates to the database. Other than hardcoding a sleep timer, some features could not be tested because they were troublesome.

In the future we will plan ahead and get started much earlier. It is also important that we all communicate our every move and establish order among who is doing what and when things are being done.