\clearpage
\section{Introduction}
The Bui’s Bayside Inn project was developed in response to a request from our client, Dr. Bui, who envisioned a web based game that combines the simplicity  of the classic card game Go Fish with modern multiplayer and social features. As part of our CS482 course, this project transforms Dr. Bui’s idea into a fully functional application. The project was designed to meet Dr. Bui’s requirements. Dr. Bui’s primary goal for the project was to create a dynamic online environment where players can enjoy Go Fish while interacting with others through social features. The game needed to allow users to create accounts, customize profiles, and participate in matches with friends or other players in private or public lobbies. Dr. Bui also requested a virtual economy to enhance the experience, enabling players to bet on games using virtual “hotel credits” and purchase profile upgrades. To ensure the game remained inclusive and enjoyable for all, administrative tools were necessary for monitoring behavior, managing disruptive users, and maintaining the overall integrity of the game environment. The Bui’s Bayside Inn game is a user friendly and visually appealing online card game built using React and Firebase. It offers secure user accounts with optional guest access for casual players. Users can join private lobbies with invite codes or participate in public games to meet new players. A virtual currency system, inspired by Dr. Bui’s vision of a “hotel credit” economy, allows players to bet on matches, adding an extra layer of excitement. The game tracks wins and losses to foster friendly competition and includes a tutorial feature to help new players learn the rules effortlessly. Social features were a key focus of the project. The game includes a friend system, private messaging, and public chat lobbies, allowing players to interact seamlessly. 

\pagebreak