\clearpage
\section{Functional Requirements}

This section outlines the requirements for the Bui’s Bayside Inn game. These requirements are presented with user stories Non-functional requirements are shown after.


\subsection{User Roles}

The following describes the types of users for the Bui’s Bayside Inn game, their technical expertise, and the level of security or access they should have. 



\subsubsection{User type}

Players are the primary users of the game. They are individuals who play Go Fish, interact with friends, and participate in the in game currency. Players are assumed to have familiarity with standard web applications. Players have access to features like account creation, gameplay, social interactions , and virtual currency transactions. They should not have access to administrative or moderation tools. Players should have secure login and logout capabilities. Data such as game statistics, friends list, and virtual currency balances must be tied to their accounts and protected from unauthorized access. Admins are moderators tasked with ensuring the platform remains safe and functional. They are expected to have a moderate level of technical expertise and familiarity with user management and moderation tools. Admins have access to both player level features and additional administrative capabilities, such as monitoring chat logs, banning users, and managing lobbies. Admin accounts must have enhanced security and the ability to view chat logs and ban users, should be restricted to verified admin accounts.

\subsection{Functional Requirements: User Stories}

This section lists all the user stories organized by user type and, within each user type, by priority.

\subsubsection{As a Player}

\textbf{ID: S1: Create Account (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to create an account
    \item \textbf{So that}: I can save my data/stats from playing Go Fish
    \item \textbf{Definition of Done}: Account created
    \item \textbf{Depends On}: N/A
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Create Account. Implement user account creation functionality, including saving user data securely. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S2: Join One Session (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to be able to join for ONE session
    \item \textbf{So that}: I can still play with my friends until I log out
    \item \textbf{Definition of Done}: Join session works
    \item \textbf{Depends On}: S1
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Guest Session. Create functionality for joining as a guest without saving user data. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S3: Account Prompt (1 point)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to be prompted to create a new account or log into a pre-existing account
    \item \textbf{So that}: I can have security and save my prior progress
    \item \textbf{Definition of Done}: Prompt appears
    \item \textbf{Depends On}: S1
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Login Prompt. Add UI and logic to display account creation or login options. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S4: Secure Logout (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to be able to securely log out of my account
    \item \textbf{So that}: I can leave the program and return later
    \item \textbf{Definition of Done}: Logout implemented
    \item \textbf{Depends On}: S1
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Logout. Implement secure logout functionality that clears session data. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S5: Main Menu Access (3 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to have a main menu
    \item \textbf{So that}: I can easily access my key features
    \item \textbf{Definition of Done}: Menu accessible
    \item \textbf{Depends On}: S1
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Main Menu. Create a central menu that links to all core functionalities. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S6: Earn Currency (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to be able to obtain currency from Go Fish games
    \item \textbf{So that}: I can make wagers or purchase other things
    \item \textbf{Definition of Done}: Currency added
    \item \textbf{Depends On}: S5
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Currency System. Implement logic to award currency for winning games. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S7: Add Friend (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to enter the username of a friend I want to add
    \item \textbf{So that}: I can have easier access to messaging/inviting them
    \item \textbf{Definition of Done}: Friend added
    \item \textbf{Depends On}: S1, S5
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Friend System. Implement friend request and addition functionality. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S8: Friend Requests (3 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to see who has requested to be my friend
    \item \textbf{So that}: I can accept/decline new requests
    \item \textbf{Definition of Done}: Requests visible
    \item \textbf{Depends On}: S7
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Friend Requests. Create a UI to view and respond to friend requests. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S9: Remove Friend (2 points)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want}: to remove unwanted friends
    \item \textbf{So that}: I can properly manage my "friends"
    \item \textbf{Definition of Done}: Friend removed
    \item \textbf{Depends On}: S7
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Remove Friend. Add functionality to remove friends from the list. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S10: Lobby Invite (3 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to invite my friend to my lobby
    \item \textbf{So that}: I can streamline the process of typing out the code
    \item \textbf{Definition of Done}: Invite works
    \item \textbf{Depends On}: S1, S5
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Lobby Invite. Implement functionality to send lobby invites to friends. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S11: Send Currency (3 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to send my friends currency
    \item \textbf{So that}: They can use it in the shop or in-game
    \item \textbf{Definition of Done}: Currency sent
    \item \textbf{Depends On}: S5, S6
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Currency Transfer. Implement functionality for sending virtual currency to friends. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S12: Access Shop (3 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: access to the shop in my main menu
    \item \textbf{So that}: I can purchase new icons or other cosmetics
    \item \textbf{Definition of Done}: Shop works
    \item \textbf{Depends On}: S5, S6
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Shop UI. Create a shop interface for purchasing cosmetic items. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S13: Change Player Icon (1 point)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want}: to change my player icon
    \item \textbf{So that}: I can express myself through cool icons
    \item \textbf{Definition of Done}: Icon change works
    \item \textbf{Depends On}: S12
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Icon Customization. Add functionality to change and save player icons. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S14: Private Messaging (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to message my friends in private
    \item \textbf{So that}: I can send specific information like lobby codes
    \item \textbf{Definition of Done}: Messaging works
    \item \textbf{Depends On}: S7
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Private Messaging. Implement a private messaging system for one-on-one communication. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S15: Lobby Chat (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to message the whole lobby
    \item \textbf{So that}: I can interact with others/ask questions
    \item \textbf{Definition of Done}: Chat visible
    \item \textbf{Depends On}: S10
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Lobby Chat. Create a chat interface for all users in a lobby. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S16: Tutorial Bot (3 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to be trained by a tutorial bot
    \item \textbf{So that}: I can learn how to play Go Fish
    \item \textbf{Definition of Done}: Tutorial functional
    \item \textbf{Depends On}: S5
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Tutorial Bot. Implement an AI-driven tutorial to teach the game rules interactively. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S17: Create Private Lobby (5 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to be able to create a private lobby
    \item \textbf{So that}: Only invited players can join
    \item \textbf{Definition of Done}: Lobby works
    \item \textbf{Depends On}: S5
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Private Lobby. Add functionality for creating password-protected or code-invite lobbies. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S18: Create Public Lobby (5 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to be able to create a public lobby
    \item \textbf{So that}: Any player can join and play
    \item \textbf{Definition of Done}: Lobby created
    \item \textbf{Depends On}: S5
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Public Lobby. Add functionality for open lobbies visible to all players. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S19: Join Lobby with Code (5 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to join a lobby using a login code
    \item \textbf{So that}: I can play with my friends online
    \item \textbf{Definition of Done}: Code login functional
    \item \textbf{Depends On}: S17, S18
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Lobby Code. Implement functionality to join lobbies using an invite code. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S20: Join Open Lobby (5 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to join an open lobby
    \item \textbf{So that}: I can play with other players online
    \item \textbf{Definition of Done}: Lobby joined
    \item \textbf{Depends On}: S17, S18
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Open Lobby. Create functionality to list and join public lobbies. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S21: Manage Players (5 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to manage other players
    \item \textbf{So that}: Games are run smoothly
    \item \textbf{Definition of Done}: Tools implemented
    \item \textbf{Depends On}: S17, S18
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Admin Tools. Build tools for player management, including editing or removing player profiles. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S22: Monitor Chat Logs (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to check on players' chat logs
    \item \textbf{So that}: I can ensure no profanity or harassment
    \item \textbf{Definition of Done}: Logs accessible
    \item \textbf{Depends On}: S15
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Chat Monitoring. Implement chat log storage and review tools for admins. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S23: Ban Players (5 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to ban misbehaving players
    \item \textbf{So that}: I can ensure the safety of others
    \item \textbf{Definition of Done}: Ban functional
    \item \textbf{Depends On}: S21
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Ban System. Create tools for admins to ban or restrict users. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S24: Ready Up for Game (1 point)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to queue up when ready to start the game
    \item \textbf{So that}: Games start when everyone is ready
    \item \textbf{Definition of Done}: Ready queue functional
    \item \textbf{Depends On}: S19, S20
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Ready Up. Add a ready-up feature to lobbies to synchronize game starts. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S25: Bet Credits (3 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to bet hotel credits during Go Fish
    \item \textbf{So that}: I can use these credits at the hotel
    \item \textbf{Definition of Done}: Betting functional
    \item \textbf{Depends On}: S6
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Betting System. Add functionality for players to wager virtual currency in-game. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S26: View Deck (2 points)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want}: to check all cards in my deck
    \item \textbf{So that}: I can plan my moves better
    \item \textbf{Definition of Done}: Deck visible
    \item \textbf{Depends On}: S5, S24
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Deck View. Implement a feature to display the player’s deck. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S27: Ask Card Rank (8 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to ask other players for a specific rank
    \item \textbf{So that}: I can add cards to my deck or Go Fish
    \item \textbf{Definition of Done}: Rank query works
    \item \textbf{Depends On}: S24, S26
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Card Query. Add gameplay logic to handle requests for specific card ranks. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: S28: View Record (1 point)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want}: to see my overall wins and losses
    \item \textbf{So that}: I can compare my record with others
    \item \textbf{Definition of Done}: Record visible
    \item \textbf{Depends On}: S1
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Win/Loss Record. Implement a feature to display player statistics. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: TT29: Stylization Of Game(3 points)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want}: to hear music in different parts of the game
    \item \textbf{So that}: I can have a more enjoyable experience
    \item \textbf{Definition of Done}: Music works
    \item \textbf{Depends On}: N/A
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Music Player. Implement background music functionality for key sections of the app. ]]
    \end{enumerate}
\end{enumerate}

\textbf{ID: TT30: Documentation (3 points)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want}: to create and maintain clear documentation for the project
    \item \textbf{So that}: Contributors can easily work with the code
    \item \textbf{Definition of Done}: Documentation complete
    \item \textbf{Depends On}: N/A
    \item Tasks:
    \begin{enumerate}
        \item Task [[ ID: Documentation. Create comprehensive documentation for project setup, architecture, and user stories. ]]
    \end{enumerate}
\end{enumerate}
